What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-25 android-stacks.tex
More improvements on introduction

Our conjecture is that several Android applicatons may be suffering from similar vulnerabilities on the exception
handling code, and that such vulnerabiliries may be leading to application crashes.

@@

When available, such information can enable different kinds of post-mortem analysis, such as:
: classify .... (get from previous versions). Previous studies on crash report analysis focused a system 
at a time. Moreover, none of them target 
a family of Android applications (which share a common core) extracting the characteristics on exceptional issues 
and looking for similar vulnerabilities on applications and underlaying platform.

In this work, we perform the first post mortem analysis of the exception stack traces embedded on issues
of all Android applications available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed the XXXX issues extracted from on XXX Android projects defined in
GitHub and XXX projects defined in Googlecode. From these issues  XXX stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK using byte code and source code analysis - which was done 
on a carefully selected subset of our initial sample (482 Android projects). Manual inspection was
used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

>>>>

Our conjecture is that several Android applicatons may be suffering from similar vulnerabilities on the exception
handling code of the applications themselves or on the underlaying platform, and that such vulnerabiliries may be leading
 to application crashes.

@@

<SUCH ISSUES INCLUDE STACK TRACES. WHAT IS THE RELATION BETWEEN STACK TRACE AND CRASH>
<stack traces are part of good issues....>
When available, such information can enable different kinds of post-mortem analysis, such as:
: classify .... (get from previous versions). Previous studies on crash report analysis focused a system 
at a time. Moreover, none of them target 
a family of Android applications (which share a common core) extracting the characteristics on exceptional issues 
and looking for similar vulnerabilities on applications and underlaying platform.

In this work, we perform the first post mortem analysis of the exception stack traces embedded on the issues
of all Android applications available in GitHub and Googlecode. Using a custom tool called ExceptionMiner,
 which we develop specifically for this study, we mine stack traces from issues across all Android projects on
GitHub and Googlecode. Overall, we analyzed the XXXX issues extracted from on XXX Android projects defined in
GitHub and XXX projects defined in Googlecode. From these issues  XXX stack traces were extracted and used as
 a source of information for our analysis. The stack trace analysis was augmented by additional information
extracted from JDK, Android SO and Android SDK using byte code and source code analysis - which was done 
on a carefully selected subset of our initial sample (482 Android projects). Manual inspection was
used to leverage the understanding of exception stack traces and support further discussions and insights.

@@

This study is built on the following assumption: the stack traces reported on issues contain 
relevant information related to application crashes. Several studies and techniques have also based on this assumption (e.g.,~\cite{sinha2009fault}~\cite{dhaliwal2011classifying}~\cite{kim2013predicting}).
